---
title: "R Notebook"
output: html_notebook
---
```{r,echo=FALSE,message=FALSE}
source("librarys.R")

```
# Initial GDP information from 2010 to 2017 by quarter
## Initial data read in
```{r, message=FALSE}
gdp_data <- read_csv(here::here("raw_data/gdp_quarterly_10-17.csv")) %>% 
  clean_names()

employment_data <- read_csv(here::here("raw_data/pop_employ_10-17.csv")) %>% 
  clean_names()

employ_industry_data <- read_csv(here::here("raw_data/employment_by_industry_10-17.csv")) %>% 
  clean_names() 

imp_exp_data <- read_csv(here::here("raw_data/imp_exports_value.csv")) %>% 
  clean_names()

```

## Data Cleaning
### GDP dataset cleaning
```{r}
gdp_cleaned <- gdp_data %>% 
  filter(measure == "HVPVOBARSA") %>% 
  mutate(period = as.yearqtr(period, format = "Q%q-%Y")) %>% 
  rename(value_in_usd = value) %>% 
  pivot_wider(names_from = measure_2, 
              values_from = value_in_usd) %>%
  clean_names() %>% 
  select(country,
         period,
         per_head_us_dollars_volume_estimates_fixed_pp_ps_oecd_reference_year_seasonally_adjusted)
```

### population over time
```{r}
population_cleaned <- employment_data %>% 
  mutate(period = as.yearqtr(period, format = "Q%q-%Y")) %>% 
  rename(people_in_k = value) %>% 
  select(country, period, subject_2, people_in_k) %>% 
  pivot_wider(names_from = subject_2, 
              values_from = people_in_k, 
              names_prefix = "k_") %>% 
  clean_names() %>% 
  select(-c(k_total_employment, k_employees, k_self_employed))

```

### employment by industry cleaned
```{r}
emp_ind_cleaned <- employ_industry_data %>% 
  filter(grepl("ETO", subject)) %>% 
  mutate(period = as.yearqtr(period, format = "Q%q-%Y")) %>% 
  rename(people_in_k = value) %>% 
  select(country, period, subject_2, people_in_k) %>% 
  pivot_wider(names_from = subject_2, 
              values_from = people_in_k, 
              names_prefix = "k_") %>% 
  clean_names() %>% 
  rename_with(~ sub("_isic_rev_4", "", .x), everything())
  
```

### Trade cleaning
```{r}
imp_exp_cleaned <- imp_exp_data %>% 
  pivot_wider(names_from = flow_2, values_from = value) %>% 
  clean_names() %>% 
  select(reporter_country, partner_country, time, exports, imports) %>% 
  mutate(time = as.yearqtr(time, format = "%Y-Q%q"))

imp_cleaned <- imp_exp_cleaned %>% 
  select(reporter_country, partner_country, time, imports) %>% 
  drop_na(imports) %>% 
  rename(imports_mill_usd = imports) %>% 
  mutate(imports_mill_usd = round(imports_mill_usd / 1000000, 2)) %>% 
  group_by(reporter_country, time) %>%  
  summarise(total_imports_mill_usd = sum(imports_mill_usd), .groups = "keep")

exp_cleaned <- imp_exp_cleaned %>% 
  select(reporter_country, partner_country, time, exports) %>% 
  drop_na(exports) %>% 
  rename(exports_mill_usd = exports) %>% 
  mutate(exports_mill_usd = round(exports_mill_usd / 1000000, 2)) %>% 
  group_by(reporter_country, time) %>%  
  summarise(total_exports_mill_usd = sum(exports_mill_usd), .groups = "keep")

# trade_clean <- imp_cleaned %>% 
#   left_join(exp_cleaned, by = c("reporter_country" = "partner_country", 
#                                 "partner_country" = "reporter_country", 
#                                 "time" = "time")) %>% 
#   filter(reporter_country != partner_country) %>% 
#   rename(reporter_partner_usd = exports,
#          partner_reporter_usd = imports)
# 

  
```

## Joining datasets together, by country and period
```{r, warning=FALSE}

gdp_pop_ind <- gdp_cleaned %>% 
  left_join(population_cleaned) %>% 
  left_join(emp_ind_cleaned) %>% 
  left_join(exp_cleaned, by = c("country" = "reporter_country", 
                                "period" = "time")) %>% 
  left_join(imp_cleaned, by = c("country" = "reporter_country", 
                                "period" = "time"))

gdp_pop_ind
```
## Data Wrangling, creating proportions

```{r}

prop <- function(x, y, dp=2){
  round((x / y) * 100, dp)
}

prop_data <- gdp_pop_ind %>% 
  mutate(
    is_uk = if_else(country == "United Kingdom", "UK", "Other OECD"),
    p_employed = prop(k_employment_total, k_total_population),
    p_agr_for_fish = prop(k_agriculture_forestry_and_fishing, 
                          k_employment_total),
    p_ind_inc_energy = prop(k_industry_including_energy, 
                            k_employment_total),
    p_ind_manuf = prop(k_of_which_manufacturing, 
                       k_employment_total),
    p_const = prop(k_construction, k_employment_total),
    prop_dist_trd_reprs_transp_accom_food_serv_activ = 
      prop(k_distrib_trade_repairs_transp_accommod_food_serv_activ, 
           k_employment_total),
    p_inf_com = prop(k_information_and_communication, 
                     k_employment_total),
    p_fin_insur = prop(k_financial_and_insurance_activities, 
                       k_employment_total),
    p_real_estate = prop(k_real_estate_activities, 
                         k_employment_total),
    p_prof_sci_techn_act_adm_supp = 
      prop(k_prof_scientif_techn_activ_admin_support_service_activ, 
           k_employment_total),
    p_pub_adm_compul_ss_ed_hhealth = 
      prop(k_public_admin_compulsory_s_s_education_human_health, 
           k_employment_total),
    p_other = prop(k_other_service_activities, 
                   k_employment_total)
    ) %>%
  rename(gdp = per_head_us_dollars_volume_estimates_fixed_pp_ps_oecd_reference_year_seasonally_adjusted,
         total_population_in_thous = k_total_population) %>% 
  select(-c(starts_with('k_')))

prop_data
```

## Calculating gdp growth and adding it to data
```{r}

growth_pc <- function(x, y, dp = 2){
  round(((x - y) / y) * 100, dp)
}

growth <- prop_data %>% 
  select(country, period, gdp) %>% 
  pivot_wider(names_from = period, values_from = gdp) %>% 
  clean_names() %>% 
  mutate(growth_perc_2010q1 = 0,
         growth_perc_2010q2 = growth_pc(x2010_q2, x2010_q1),
         growth_perc_2010q3 = growth_pc(x2010_q3, x2010_q2),
         growth_perc_2010q4 = growth_pc(x2010_q4, x2010_q3),
         growth_perc_2011q1 = growth_pc(x2011_q1, x2010_q4),
         growth_perc_2011q2 = growth_pc(x2011_q2, x2011_q1),
         growth_perc_2011q3 = growth_pc(x2011_q3, x2011_q2),
         growth_perc_2011q4 = growth_pc(x2011_q4, x2011_q3),
         growth_perc_2012q1 = growth_pc(x2012_q1, x2011_q4),
         growth_perc_2012q2 = growth_pc(x2012_q2, x2012_q1),
         growth_perc_2012q3 = growth_pc(x2012_q3, x2012_q2),
         growth_perc_2012q4 = growth_pc(x2012_q4, x2012_q3),
         growth_perc_2013q1 = growth_pc(x2013_q1, x2012_q4),
         growth_perc_2013q2 = growth_pc(x2013_q2, x2013_q1),
         growth_perc_2013q3 = growth_pc(x2013_q3, x2013_q2),
         growth_perc_2013q4 = growth_pc(x2013_q4, x2013_q3),
         growth_perc_2014q1 = growth_pc(x2014_q1, x2013_q4),
         growth_perc_2014q2 = growth_pc(x2014_q2, x2014_q1),
         growth_perc_2014q3 = growth_pc(x2014_q3, x2014_q2),
         growth_perc_2014q4 = growth_pc(x2014_q4, x2014_q3),
         growth_perc_2015q1 = growth_pc(x2015_q1, x2014_q4),
         growth_perc_2015q2 = growth_pc(x2015_q2, x2015_q1),
         growth_perc_2015q3 = growth_pc(x2015_q3, x2015_q2),
         growth_perc_2015q4 = growth_pc(x2015_q4, x2015_q3),
         growth_perc_2016q1 = growth_pc(x2016_q1, x2015_q4),
         growth_perc_2016q2 = growth_pc(x2016_q2, x2016_q1),
         growth_perc_2016q3 = growth_pc(x2016_q3, x2016_q2),
         growth_perc_2016q4 = growth_pc(x2016_q4, x2016_q3),
         growth_perc_2017q1 = growth_pc(x2017_q1, x2016_q4),
         growth_perc_2017q2 = growth_pc(x2017_q2, x2017_q1),
         growth_perc_2017q3 = growth_pc(x2017_q3, x2017_q2),
         growth_perc_2017q4 = growth_pc(x2017_q4, x2017_q3)) %>%
  select(country, starts_with("growth")) %>% 
  pivot_longer(cols = starts_with("growth"), names_to = "period", 
               values_to = "gdp_perc_growth", names_prefix = "growth_perc_") %>% 
  mutate(period = as.yearqtr(period, format = "%Yq%q"))

prop_data_growth_pc <- prop_data %>% 
  left_join(growth)
```

## Plots 
### UK GDP vs other countries
```{r}
prop_data %>% 
  ggplot(aes(x = period, y = gdp)) +
  geom_line(aes(colour = country), show.legend = FALSE) +
  geom_line(data = (prop_data %>% filter(country == "United Kingdom")), 
            size = 2, colour = "red")

```
### GDP Growth Comparison
```{r}

prop_data_growth_pc %>% 
  ggplot(aes(x = period, y = gdp_perc_growth)) +
  geom_line(aes(group = country), colour = "grey50", show.legend = FALSE) +
  geom_line(data = (prop_data_growth_pc %>% filter(country == "United Kingdom")), 
            size = 2, colour = "red") +
  ylim(NA, 7.5) +
  xlim(2010.1, NA)


```

### working out countries with better average per quarter GDP growth than the UK
```{r}

uk_mean_gdp_growth <- prop_data_growth_pc %>% 
  group_by(country) %>% 
  summarise(mean_gdp_growth = mean(gdp_perc_growth)) %>% 
  filter(country == "United Kingdom") %>% 
  select(mean_gdp_growth) %>% 
  pull()

uk_mean_gdp <- prop_data_growth_pc %>% 
  group_by(country) %>% 
  summarise(mean_gdp = mean(gdp)) %>% 
  filter(country == "United Kingdom") %>% 
  select(mean_gdp) %>% 
  pull()

ctry_higher_mean_growth <- prop_data_growth_pc %>% 
  group_by(country) %>% 
  summarise(mean_gdp_growth = mean(gdp_perc_growth)) %>% 
  filter(mean_gdp_growth >= uk_mean_gdp_growth) %>% 
  select(country) %>% 
  pull() %>% 
  as.list()

ctry_higher_mean_gdp <- prop_data_growth_pc %>% 
  group_by(country) %>% 
  summarise(mean_gdp = mean(gdp)) %>% 
  filter(mean_gdp >= uk_mean_gdp) %>% 
  select(country) %>% 
  pull() %>% 
  as.list()



```

### Plot showing average UK GDP growth vs other countries
```{r}

prop_data_growth_pc %>% 
  # filter(period > "2013 Q4") %>% 
  group_by(country, is_uk) %>% 
  summarise(average_gdp_growth = mean(gdp_perc_growth)) %>% 
  # filter(average_gdp_growth >= 0.415625) %>% 
  ggplot(aes(x = fct_reorder(country, average_gdp_growth), average_gdp_growth)) +
  geom_col(aes(fill = is_uk)) +
  coord_flip()

```

# Model building
## Country Split model
### Test train set using country
```{r}
set.seed(523)
n_data1 <- prop_data_growth_pc %>% 
  distinct(country) %>% 
  nrow()

countrys <- prop_data_growth_pc %>% 
  distinct(country) %>% 
  mutate(country_num = 1:n_data1)

countrys_index <- tibble(sample(n_data1, size = n_data1 * 0.3)) %>% 
  clean_names()

country_name_index <- countrys_index %>%
  left_join(countrys, 
            by = c("sample_n_data1_size_n_data1_0_3" = "country_num")) %>% 
  select(country) %>% 
  pull()
  

gdp_country_test <- prop_data_growth_pc %>% 
  filter(country %in% country_name_index)

gdp_country_train <- prop_data_growth_pc %>% 
  filter(!country %in% country_name_index)

gdp_country_train_tidy <- gdp_country_train %>% 
  select(-c(country, period, is_uk, gdp_perc_growth, total_exports_mill_usd, 
            total_imports_mill_usd))

```

### Build Model
```{r}
glmulti_country_fit <- glmulti(
  gdp ~ ., 
  data = gdp_country_train_tidy,
  level = 2, # 2 = include pairwise interactions, 1 = main effects only (main effect = no pairwise interactions)
  minsize = 0, # no min size of model
  maxsize = -1, # -1 = no max size of model
  marginality = TRUE, # marginality here means the same as 'strongly hierarchical' interactions, i.e. include pairwise interactions only if both predictors present in the model as main effects.
  method = "g", # the problem is too large for exhaustive search, so search using a genetic algorithm
  crit = bic, # criteria for model selection is BIC value (lower is better)
  plotty = FALSE, # don't plot models as function runs
  report = FALSE, # do produce reports as function runs
  chunks = 8,
  confsetsize = 10, # return best 100 solutions
  fitfunction = lm  # fit using the `lm` function
)

print(glmulti_country_fit)
 

```

### Check AR2 and coeffs
```{r}
train_country_model = lm(
  gdp ~ 1 + total_population_in_thous + p_employed + p_agr_for_fish +                                                                 
    p_ind_inc_energy + p_ind_manuf + p_const + 
    prop_dist_trd_reprs_transp_accom_food_serv_activ + p_inf_com + 
    p_fin_insur + p_real_estate + p_prof_sci_techn_act_adm_supp + 
    p_pub_adm_compul_ss_ed_hhealth + p_other + 
    p_employed:total_population_in_thous + 
    p_ind_inc_energy:total_population_in_thous + 
    p_ind_manuf:total_population_in_thous + p_ind_manuf:p_employed + 
    p_const:p_agr_for_fish + p_const:p_ind_inc_energy + 
    prop_dist_trd_reprs_transp_accom_food_serv_activ:total_population_in_thous +
    prop_dist_trd_reprs_transp_accom_food_serv_activ:p_agr_for_fish +
    prop_dist_trd_reprs_transp_accom_food_serv_activ:p_ind_inc_energy + 
    prop_dist_trd_reprs_transp_accom_food_serv_activ:p_const + 
    p_inf_com:p_employed + p_inf_com:p_ind_manuf + p_inf_com:p_const + 
    p_inf_com:prop_dist_trd_reprs_transp_accom_food_serv_activ + 
    p_fin_insur:total_population_in_thous + p_fin_insur:p_agr_for_fish +     
    p_fin_insur:p_const + p_fin_insur:p_inf_com + p_real_estate:p_employed + 
    p_real_estate:p_agr_for_fish + p_real_estate:p_ind_manuf + 
    p_real_estate:p_const + 
    p_real_estate:prop_dist_trd_reprs_transp_accom_food_serv_activ + 
    p_real_estate:p_inf_com + p_real_estate:p_fin_insur + 
    p_prof_sci_techn_act_adm_supp:total_population_in_thous + 
    p_prof_sci_techn_act_adm_supp:p_employed + 
    p_prof_sci_techn_act_adm_supp:p_ind_inc_energy + 
    p_prof_sci_techn_act_adm_supp:p_const + 
    p_prof_sci_techn_act_adm_supp:prop_dist_trd_reprs_transp_accom_food_serv_activ + 
    p_prof_sci_techn_act_adm_supp:p_inf_com + 
    p_prof_sci_techn_act_adm_supp:p_fin_insur + 
    p_prof_sci_techn_act_adm_supp:p_real_estate + 
    p_pub_adm_compul_ss_ed_hhealth:total_population_in_thous + 
    p_pub_adm_compul_ss_ed_hhealth:p_employed + 
    p_pub_adm_compul_ss_ed_hhealth:p_agr_for_fish +
    p_pub_adm_compul_ss_ed_hhealth:p_ind_inc_energy + 
    p_pub_adm_compul_ss_ed_hhealth:prop_dist_trd_reprs_transp_accom_food_serv_activ + 
    p_pub_adm_compul_ss_ed_hhealth:p_inf_com + 
    p_pub_adm_compul_ss_ed_hhealth:p_fin_insur +
    p_pub_adm_compul_ss_ed_hhealth:p_real_estate + 
    p_other:total_population_in_thous +
    p_other:p_agr_for_fish + p_other:p_ind_inc_energy + p_other:p_ind_manuf + 
    p_other:prop_dist_trd_reprs_transp_accom_food_serv_activ + 
    p_other:p_inf_com + p_other:p_fin_insur + p_other:p_real_estate +
    p_other:p_prof_sci_techn_act_adm_supp,                 
  data = gdp_country_train_tidy)

train_country_model %>% 
  summary()

train_country_model %>% 
  autoplot()
```


### Check on Test data
```{r}

gdp_country_test_tidy <- gdp_country_test %>% 
  select(-c(country, period, is_uk, gdp_perc_growth, total_exports_mill_usd, 
            total_imports_mill_usd))

test_country_model = lm(
  gdp ~ 1 + total_population_in_thous + p_employed + p_agr_for_fish +                                                                 
    p_ind_inc_energy + p_ind_manuf + p_const + 
    prop_dist_trd_reprs_transp_accom_food_serv_activ + p_inf_com + 
    p_fin_insur + p_real_estate + p_prof_sci_techn_act_adm_supp + 
    p_pub_adm_compul_ss_ed_hhealth + p_other + 
    p_employed:total_population_in_thous + 
    p_ind_inc_energy:total_population_in_thous + 
    p_ind_manuf:total_population_in_thous + p_ind_manuf:p_employed + 
    p_const:p_agr_for_fish + p_const:p_ind_inc_energy + 
    prop_dist_trd_reprs_transp_accom_food_serv_activ:total_population_in_thous +
    prop_dist_trd_reprs_transp_accom_food_serv_activ:p_agr_for_fish +
    prop_dist_trd_reprs_transp_accom_food_serv_activ:p_ind_inc_energy + 
    prop_dist_trd_reprs_transp_accom_food_serv_activ:p_const + 
    p_inf_com:p_employed + p_inf_com:p_ind_manuf + p_inf_com:p_const + 
    p_inf_com:prop_dist_trd_reprs_transp_accom_food_serv_activ + 
    p_fin_insur:total_population_in_thous + p_fin_insur:p_agr_for_fish +     
    p_fin_insur:p_const + p_fin_insur:p_inf_com + p_real_estate:p_employed + 
    p_real_estate:p_agr_for_fish + p_real_estate:p_ind_manuf + 
    p_real_estate:p_const + 
    p_real_estate:prop_dist_trd_reprs_transp_accom_food_serv_activ + 
    p_real_estate:p_inf_com + p_real_estate:p_fin_insur + 
    p_prof_sci_techn_act_adm_supp:total_population_in_thous + 
    p_prof_sci_techn_act_adm_supp:p_employed + 
    p_prof_sci_techn_act_adm_supp:p_ind_inc_energy + 
    p_prof_sci_techn_act_adm_supp:p_const + 
    p_prof_sci_techn_act_adm_supp:prop_dist_trd_reprs_transp_accom_food_serv_activ + 
    p_prof_sci_techn_act_adm_supp:p_inf_com + 
    p_prof_sci_techn_act_adm_supp:p_fin_insur + 
    p_prof_sci_techn_act_adm_supp:p_real_estate + 
    p_pub_adm_compul_ss_ed_hhealth:total_population_in_thous + 
    p_pub_adm_compul_ss_ed_hhealth:p_employed + 
    p_pub_adm_compul_ss_ed_hhealth:p_agr_for_fish +
    p_pub_adm_compul_ss_ed_hhealth:p_ind_inc_energy + 
    p_pub_adm_compul_ss_ed_hhealth:prop_dist_trd_reprs_transp_accom_food_serv_activ + 
    p_pub_adm_compul_ss_ed_hhealth:p_inf_com + 
    p_pub_adm_compul_ss_ed_hhealth:p_fin_insur +
    p_pub_adm_compul_ss_ed_hhealth:p_real_estate + 
    p_other:total_population_in_thous +
    p_other:p_agr_for_fish + p_other:p_ind_inc_energy + p_other:p_ind_manuf + 
    p_other:prop_dist_trd_reprs_transp_accom_food_serv_activ + 
    p_other:p_inf_com + p_other:p_fin_insur + p_other:p_real_estate +
    p_other:p_prof_sci_techn_act_adm_supp,                 
  data = gdp_country_test_tidy)

test_country_model %>% 
  summary()

test_country_model %>% 
  autoplot()

```

### Plot Predictions against observations

```{r}
gdp_country_test %>% 
  # filter(country == "Australia") %>% 
  add_predictions(test_country_model) %>%
  add_residuals(test_country_model) %>% 
  select(country, period, gdp, pred, resid) %>% 
  ggplot(aes(x = period)) +
  geom_line(aes(y = gdp, group = country), alpha = .2) +
  geom_line(aes(y = pred, group = country), colour = "red") +
  geom_smooth(method = "lm", aes(y = pred, group = country))
```
### Kfold validation on country model
```{r}

full_data_tidy <- prop_data_growth_pc %>% 
  select(-c(country, period, is_uk, gdp_perc_growth, total_exports_mill_usd, 
            total_imports_mill_usd)) %>% 
  drop_na()

cv_100fold <- trainControl(method = "cv", #cross validation
                          number = 100, # 10 folds
                          savePredictions = TRUE) # save all predictions

period_model_w_kfold <- train(gdp ~ 1 + total_population_in_thous + total_exports_mill_usd + 
    total_imports_mill_usd + p_employed + p_agr_for_fish + p_ind_inc_energy + 
    p_ind_manuf + p_const + prop_dist_trd_reprs_transp_accom_food_serv_activ + 
    p_inf_com + p_fin_insur + p_real_estate + p_prof_sci_techn_act_adm_supp + 
    p_pub_adm_compul_ss_ed_hhealth + p_other + 
    total_exports_mill_usd:total_population_in_thous + 
    total_imports_mill_usd:total_population_in_thous + 
    p_employed:total_population_in_thous + p_employed:total_imports_mill_usd + 
    p_agr_for_fish:total_imports_mill_usd + 
    p_ind_inc_energy:total_population_in_thous + 
    p_ind_manuf:total_exports_mill_usd + p_ind_manuf:p_agr_for_fish + 
    p_const:total_exports_mill_usd + p_const:p_employed + 
    prop_dist_trd_reprs_transp_accom_food_serv_activ:p_agr_for_fish + 
    p_inf_com:total_population_in_thous + p_inf_com:total_exports_mill_usd + 
    p_inf_com:p_agr_for_fish + p_inf_com:p_ind_manuf + p_inf_com:p_const + 
    p_inf_com:prop_dist_trd_reprs_transp_accom_food_serv_activ + 
    p_fin_insur:total_population_in_thous + p_fin_insur:total_imports_mill_usd + 
    p_fin_insur:p_employed + p_fin_insur:p_ind_manuf + 
    p_fin_insur:prop_dist_trd_reprs_transp_accom_food_serv_activ + 
    p_real_estate:total_exports_mill_usd + 
    p_real_estate:total_imports_mill_usd + p_real_estate:p_employed + 
    p_real_estate:p_agr_for_fish + p_real_estate:p_inf_com + 
    p_prof_sci_techn_act_adm_supp:total_population_in_thous + 
    p_prof_sci_techn_act_adm_supp:total_exports_mill_usd + 
    p_prof_sci_techn_act_adm_supp:p_employed + 
    p_prof_sci_techn_act_adm_supp:p_agr_for_fish + 
    p_prof_sci_techn_act_adm_supp:p_ind_manuf + 
    p_prof_sci_techn_act_adm_supp:prop_dist_trd_reprs_transp_accom_food_serv_activ + 
    p_prof_sci_techn_act_adm_supp:p_inf_com +
    p_prof_sci_techn_act_adm_supp:p_fin_insur + 
    p_pub_adm_compul_ss_ed_hhealth:total_imports_mill_usd + 
    p_pub_adm_compul_ss_ed_hhealth:p_employed + 
    p_pub_adm_compul_ss_ed_hhealth:p_agr_for_fish + 
    p_pub_adm_compul_ss_ed_hhealth:p_ind_inc_energy + 
    p_pub_adm_compul_ss_ed_hhealth:p_const + 
    p_pub_adm_compul_ss_ed_hhealth:p_inf_com + 
    p_pub_adm_compul_ss_ed_hhealth:p_fin_insur + 
    p_pub_adm_compul_ss_ed_hhealth:p_real_estate + 
    p_pub_adm_compul_ss_ed_hhealth:p_prof_sci_techn_act_adm_supp + 
    p_other:total_exports_mill_usd + p_other:p_ind_inc_energy + 
    p_other:p_prof_sci_techn_act_adm_supp,
               data = full_data_tidy,
               trControl = cv_100fold,
               method = "lm")


period_model_w_kfold$pred
period_model_w_kfold$resample

mean(period_model_w_kfold$resample$RMSE)
mean(period_model_w_kfold$resample$Rsquared)
```

## Period Split model
### Test Train set
```{r}
set.seed(12)

n_data <- nrow(prop_data_growth_pc)

# make a test index
test_index <- sample(1:n_data, size = n_data * 0.2)

# use test index to create test & training datasets
gdp_period_test <- slice(prop_data_growth_pc, test_index)
gdp_period_train <- slice(prop_data_growth_pc, -test_index)



gdp_period_train_tidy <- gdp_period_train %>% 
  select(-c(country, period, is_uk))

```

#### Build Model
```{r}

glmulti_period_fit <- glmulti(
  gdp ~ ., 
  data = gdp_period_train_tidy,
  level = 1, # 2 = include pairwise interactions, 1 = main effects only (main effect = no pairwise interactions)
  minsize = 0, # no min size of model
  maxsize = -1, # -1 = no max size of model
#  marginality = TRUE, # marginality here means the same as 'strongly hierarchical' interactions, i.e. include pairwise interactions only if both predictors present in the model as main effects.
  method = "g", # the problem is too large for exhaustive search, so search using a genetic algorithm
  crit = bic, # criteria for model selection is BIC value (lower is better)
  plotty = FALSE, # don't plot models as function runs
  report = FALSE, # do produce reports as function runs
  chunks = 8,
  confsetsize = 10, # return best 100 solutions
  fitfunction = lm  # fit using the `lm` function
)

glmulti_period_fit %>% 
    summary()
```

### Check AR2 and coeffs
```{r}

train_period_model = lm(gdp ~ total_population_in_thous+total_exports_mill_usd+
                   total_imports_mill_usd+p_employed+p_agr_for_fish+p_inf_com+
                   p_fin_insur+p_real_estate+p_prof_sci_techn_act_adm_supp+
                   p_pub_adm_compul_ss_ed_hhealth,
                 data = gdp_period_train)

train_period_model %>% 
  summary()

```
### Check on Test Data
```{r}
gdp_period_test_tidy <- gdp_period_test %>% 
  select(-c(country, period, is_uk))

test_period_model = lm(gdp ~ total_population_in_thous+total_exports_mill_usd+
                   total_imports_mill_usd+p_employed+p_agr_for_fish+p_inf_com+
                   p_fin_insur+p_real_estate+p_prof_sci_techn_act_adm_supp+
                   p_pub_adm_compul_ss_ed_hhealth,
                 data = gdp_period_test_tidy)

test_period_model %>% 
  summary()
```


### Plot Predictions against observations
```{r}

gdp_period_test %>% 
  # filter(country == "Australia") %>% 
  add_predictions(train_period_model) %>%
  add_residuals(train_period_model) %>% 
  select(country, period, gdp, pred, resid) %>% 
  ggplot(aes(x = period)) +
  geom_line(aes(y = gdp, group = country), alpha = .2) +
  geom_line(aes(y = pred, group = country), colour = "red")

```
### Kfold validation on Period model
```{r}

full_data_tidy <- prop_data_growth_pc %>% 
  select(-c(country, period, is_uk)) %>% 
  drop_na()

cv_100fold <- trainControl(method = "cv", #cross validation
                          number = 10, # 10 folds
                          savePredictions = TRUE) # save all predictions

model_w_kfold <- train(gdp ~ total_population_in_thous+total_exports_mill_usd+
                   total_imports_mill_usd+p_employed+p_agr_for_fish+p_inf_com+
                   p_fin_insur+p_real_estate+p_prof_sci_techn_act_adm_supp+
                   p_pub_adm_compul_ss_ed_hhealth,
                   data = full_data_tidy,
               trControl = cv_100fold,
               method = "lm")


model_w_kfold$pred
model_w_kfold$resample

mean(model_w_kfold$resample$RMSE)
mean(model_w_kfold$resample$Rsquared)
```

